Paper Analysis

### 2025-04-28 Paper_WriteUp/Paper_Plots.qmd
cleaning fig4 chunk, getting rid of stuff we don't use

```{r player level parameters for 17-19}
#| eval: false
player_id <- as_tibble(bullet_17_19) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

@@

## see how many contain 0
player_pars |> 
  group_by(player_name, param) |> 
  filter(param == 2) |> 
  summarise(lower = quantile(value, prob = 0.025),
            upper = quantile(value, prob = 0.975)) |> 
  mutate(contain_zero = ifelse(upper > 0 & lower < 0,
                         1, 0)) |> 
  filter(contain_zero == 0)
```

```{r figure 4 left}
winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.125, 0.125)) +
  theme_single_y()

>>>>

```{r figure 4 left}
#| eval: false
player_id <- as_tibble(bullet_17_19) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

@@

#plot
winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.125, 0.125)) +
  theme_single_y()
